---
title: "Lab 01 - Hello R"
author: "Ye Dam Yi"
date: "2/1/2021"
output: 
  html_document: 
    highlight: zenburn
    theme: cerulean
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

In the dataframe datasaurus_dozen are 1846 rows and 3 columns. The variables included are dataset, x, and y. 


### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=5, fig.width=7}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

library("ggplot2")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
The correlation coefficient is -.06447.

### Exercise 3



```{r plot-star, fig.height=5, fig.width=7}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) + geom_point()

```


```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
The value of the correlation coefficient is not that different from the one for the dino dataset. 

### Exercise 4


```{r plot-circle, fig.height=5, fig.width=7}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) + geom_point()


```

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```
The correlation coefficient is close to the one found for the dino dataset.

### Exercise 5


```{r plot-all, fig.height=20, fig.width=25}

ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")

```


```{r cor-all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```

